Dynamics of Laterally Propagating Flames in X-ray Bursts. III. Comparing Hotspot Evolution in Two and Three Dimensions

### 2022-02-06 xrb3/paper.tex
more paper writing

%======================================================================
% Abstract and Keywords
%======================================================================
\begin{abstract}
We continue to investigate laterally propagating flames in XRBs,
comparing the dynamics between two- and three-dimensions.
\end{abstract}

@@

In \citet{harpole:2021}, we explored several different rotation rates
and initial model thermal structures.  We found that a model with a
neutron star crust temperature of $3\times 10^8~\mathrm{K}$ resulted
in a flame that accelerated quickly as it spread across the neutron
star surface.  We adopt this model for the 3D simulation presented
here, since it requires the least amount of simulation time to yield a
developed flame.  Moving to 3D is very expensive, so to further reduce
the computational expense, we use a slightly lower resolution of 25 cm
instead of 20 cm from \citet{harpole:2021}.  We pick a rotation rate
of 1000 Hz.

@@

We have extended our simulation framework to three-dimensions, and
explored the differences between a two-dimensional axisymmetric
simulation and a fully three-dimensional simulation.

>>>>

%======================================================================
% Abstract and Keywords
%======================================================================
\begin{abstract}
We continue to investigate laterally propagating flames in XRBs,
comparing the early evolution and structure of a burning hotspot
between two- and three-dimensions.
\end{abstract}

@@

In \citet{harpole:2021}, we explored several different rotation rates
and initial model thermal structures.  We found that a model with a
neutron star crust temperature of $3\times 10^8~\mathrm{K}$ resulted
in a flame that accelerated quickly as it spread across the neutron
star surface.  We adopt this model for the 3D simulation presented
here, since it requires the least amount of simulation time to yield a
developed flame.

Moving to 3D is very expensive, so to further reduce the computational
expense, we use a slightly lower resolution of 25 cm instead of 20 cm
from \citet{harpole:2021}.  We pick a rotation rate of 1000 Hz.
Because the hotspot is placed in the center of the domain, the size of
the domain also becomes a constraint, and as a result, the evolution
time we can reach will become limited by the time it takes the burning
to approach the edge of the domain.  As a result, we focus here on the
early evolution.

@@

We have extended our simulation framework to three-dimensions, and
explored the differences between a two-dimensional axisymmetric
simulation and a fully three-dimensional hydrodynamical simulation.

The main limitation of this study is that computational resources
limited the size of the domain and resolution we could use.  To
improve simulations for the future, there are several avenues to
pursue.  First, the main expense of the current simulations is the
reaction network.  We need to work more on optimization of the
network.  Second, while additional resolution will be expensive, we
can go higher order, as demonstrated with the 4th order accurate
coupling of hydro, diffusion, and reactions in \cite{castro-sdc}.  The
main outstanding issue with applying that work to the present problem
is the multilevel time integration.
